\documentclass[a4,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm, top=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf, %SourceSansPro-Bold.otf
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}

%%%% Define New Commands
\usepackage[style=nature, maxbibnames=3]{biblatex}
\addbibresource{Publications.bib}

%%%% Bold Name in Publications
\renewcommand*{\mkbibnamegiven}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

%%%% Set Sections formatting
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}

% \newcommand{\subtextit}[1]{\vspace{0.15cm}
% \textit{ #1 \vspace{-0.2cm}} }

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}


%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]


\begin{document}

\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large Tunisia \\
            \large +21699500924 \\
            \large \href{mailto:sirajeddineaissa@protonmail.com}{sirajeddineaissa@protonmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\HUGE Sirajeddine Aissa} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Full-stack Developer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large  %Willing to Relocate
            {\href{https://www.linkedin.com/in/sirajeddineaissa}{\small \textbf {linkedin.com/in/sirajeddineaissa}} } \\
            \href{https://sirajeddineaissa.vercel.app}{\small \textbf {Portfolio}}
            \href{https://github.com/sirajeddineaissa}{\small \textbf {github.com/sirajeddineaissa}}
    \end{minipage}   
    
\vspace{-0.15cm} 
\end{center}


\section{Education }
\subsection*{Industrial Engineering {\normalsize \normalfont   at the National Institute of Applied Science and Technology (INSAT)} \hfill September 2019 - Present} 
\vspace{0.1cm}
\subsection*{Baccalaureate in Computer Science {\normalsize \normalfont   achieved with a score of 16.30/20, ranked 12th countrywide. } \hfill September 2018 - June 2019} 
\vspace{0.2cm}


\section{Work Experience}
\subsection*{ Full-stack Developer \hfill December 2021 - February 2022} 
\subtext{CONSULTING @ LOGICIELS ET SYSTÈMES\hfill } 
    \begin{zitemize}
        \item  Development of a Web App for the needs of Accon-rvs, an accounting platform built with Angular, Laravel and MySQL, running through a Jenkins pipeline.
    \end{zitemize}
    






\section{Volunteering Experience}

\subsection*{Media and Communication Manager \hfill March 2022 - July 2022} 
\subtext{National Robotics Weekend 4.0\hfill } 
    \begin{zitemize}
        \item Responsible for re-branding the National Robotics Weekend 4.0's theme (It's a yearly congress abbreviated as NRW 4.0, hosted by one of IEEE's society chapters (The Robotics & Automation Society)).
        \item Responsible for creating the graphic design assets related to the event.
        \item Responsible for moderating the event's social media.
    \end{zitemize}

\subsection*{Web Designer \hfill March 2022 - April 2022} 
\subtext{IEEE INSAT Student Branch\hfill } 
    \begin{zitemize}
        \item Helped in designing the website's prototype for R8 IEEE Students and Young Professional Congress Tunis 2022, an international event related to IEEE and occurs once every 2 years.
        \item NOTE : The website may take some time to fully load because of server-side problems related to the IEEE Tunisia Section server.
                \item \href{https://r8syp.ieee.tn/}{\small \textbf {Check the website here!}}

    \end{zitemize}
    
\subsection*{Webmaster \hfill August 2021 - Present} 
\subtext{IEEE INSAT Student Branch\hfill } 
    \begin{zitemize}
        \item   Head of the Webmasters' department.
        \item  Responsible for creating and managing IEEE INSAT's Student Branch website as well as monitoring and supervising other Webmasters in IEEE's chapters.
                        

    \end{zitemize}
    
\subsection*{ Front-end Engineer \hfill November 2021 - February 2022} 
\subtext{Junior Entreprise INSAT\hfill } 
    \begin{zitemize}
        \item  Executed front-end tasks with React within a platform that facilitates the affiliation of rural women to the social and health coverage system and helps leverage the payment of expenses remotely.
        
    \end{zitemize}

\subsection*{Competitive Programming Problem Setter \hfill November 2020 - April 2021} 
\subtext{INSAT ACM Student Chapter \hfill } 
    \begin{zitemize}
        \item  Contributed to the SheSolves 2021 programming event hosted at the National Institute of Applied Science and Technology, by creating and testing competitive programming problems.
         \item \href{https://github.com/sirajeddineaissa/SheSolves2021-INSAT}{\small \textbf {Check the GitHub repository here!}}
    \end{zitemize}
  


\section{Projects} %% (Or "Research", select as appropriate)
\subsection*{GitHub Repo Search {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item A web-based solution that allows users to search GitHub profiles and go through their GitHub repositories. It also allows users to view some of the data related to each repository (title, description, stars...) and redirect them to its URL.
        \item Tech used: React, Chakra UI
         \item \href{https://mvst-project.netlify.app/}{\small \textbf {Check the project here!}}
    \end{zitemize}

\subsection*{WipeLacer {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item A type-racing web app where the user is provided with Start and Practice sections where they're prompted to write down generated quotes in a certain amount of time and get their WPM/Accuracy results. Each user will have their matches and results saved. A future online implementation will be considered.
        \item Tech used: React, Firebase
         \item \href{https://wipelacer.vercel.app}{\small \textbf {Check the project here!}}
    \end{zitemize}


\subsection*{Reddiper {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item A desktop app that scrapes content from reddit and saves it locally (for the moment, only images).
        \item  Tech used: OpenCV, PySimpleGUI, Reddit API Wrapper
    \end{zitemize}
\subsection*{IEEE INSAT Student Branch 2022 Website {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item Tech used: React
         \item NOTE : The website may take some time to fully load because of server-side problems related to the IEEE Tunisia Section server.
        \item \href{https://insat.ieee.tn}{\small \textbf {Check the project here!}}
       
    \end{zitemize}

    
   
\subsection*{Web Chat {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item Established an online web chat app with only Google accounts.
        \item Tech used: React, Firebase
        \item \href{https://webchat-37001.firebaseapp.com/}{\small \textbf {Check the project here!}}
        
    \end{zitemize}
   



\subsection*{MIMO {\normalsize\normalfont} \hfill} 
    \begin{zitemize}
        \item A Memory Card Game.
                \item Tech used: Vanilla JavaScript

    \end{zitemize}



\section{Programming Techstack}
\begin{tabular}{p{11em} p{1em} p{43em}}
\hskills{Languages }&  & JavaScript, TypeScript, C++, Python, SQL, Bash \\
\hskills{Technologies} &  & React.js, Next.js, Node.js, Express.js, Firebase, \\
\hskills{Data Science / ML} &  & Pandas, Numpy, Matplotlib  \\
\hskills{Version Control} &  & Git, GitHub \\
\hskills{Scrum/Agile Solutions} &  & Trello \\
\hskills{Graphic and UI/UX Design} &  & Adobe Photoshop, Adobe Illustrator, Figma, Adobe XD 
\\


\end{tabular}

\section{Spoken Languages}
\begin{tabular}{p{11em} p{1em} p{43em}}
\hskills{English}&  &  Fluent\\
\hskills{French}&  &  Fluent\\
\hskills{Arabic}&  &  Native\\
\hskills{German}&  &  Basic\\



\end{tabular}
\vspace{-0.2cm}

\end{document}